S2. Additional figures and table

### 2022-02-19 Manuscript/Manuscript.Rmd
update for arxiv submission

---
title: An open-source integrated framework for the automation of citation collection and screening in systematic reviews. 
authors:
  - name: Angelo D'Ambrosio
    department: Institute for Infection Prevention and Hospital Hygiene
    affiliation: Freiburg University Hospital
    location: Freiburg, Germany
    email: angelo.d.ambrosio@uniklinik-freiburg.de; a.dambrosioMD@gmail.com
  - name: Hajo Grundmann
    department: Institute for Infection Prevention and Hospital Hygiene
    affiliation: Freiburg University Hospital
    location: Freiburg, Germany
    email: hajo.grundmann@uniklinik-freiburg.de
  - name: Tjibbe Donker
    department: Institute for Infection Prevention and Hospital Hygiene
    affiliation: Freiburg University Hospital
    location: Freiburg, Germany
    email: tjibbe.donker@uniklinik-freiburg.de
abstract: |
  The exponential and prolific growth of published original scientific contributions makes secondary literature abridgements increasingly demanding.
  We introduce a new open-source framework for systematic reviews that significantly reduces time and human resource allocation for text identification, collection, and screening of scientific literature.\
  The framework provides three main tools:
  1) An automatic citation search engine and manager that allows collecting records from multiple citation databases (Pubmed, WOS, SCOPUS, EMBASE, IEEE) with a unified query syntax
  2) A citation screening tool based on Bayesian active machine learning and natural language processing that requires users feedback only on uncertain classifications to iteratively increase predictive accuracy and
  3) A semi-automatic, data-driven query generator to create new search queries from existing reviewed citation data sets.\
  The framework was tested on an example topic to collect and screen citations of related scientific production.
  To evaluate the performance of the active machine learning classifier,
  we estimated the median posterior sensitivity and efficiency [90% Credible Intervals] using Bayesian simulation to predict the distribution of potentially relevant matches among the records not manually reviewed.\
  A total of 17,755 unique records were collected through the framework citation manager;
  101 of 766 records were found to be relevant after manual evaluation,
  while the rest were excluded by automatic classification;
  the theorethical efficiency was 95.6% [95.3%, 95.7%] with a sensitivity of 100% [93.5%, 100%].\
  A new search query was generated from the labelled dataset, and 82,579 additional records were collected;
  only 567 records required human review after automatic screening, and six additional positive matches were found.
  Including the additional records, the overall expected sensitivity decreased to 97.3% [73.8%, 100%] while the efficiency increased to 98.6% [98.2%, 98.7%].\
  For large studies, the framework can significantly reduce the human resources required to conduct systematic reviews
  by simplifying citation collection and screening while demonstrating exceptional sensitivity.
  Such tool can improve the standardization and repeatability of systematic reviews.
keywords:
  - Systematic review automation
  - Citation management
  - Online data collection
  - Active machine learning
  - Natural language processing
  - Bayesian modeling
bibliography: references.bib
lang: en-GB
output: 
  rticles::arxiv_article:
    number_sections: no
    keep_tex: true
    includes:
      in_header: header.tex
---

>>>>

---
title: An open-source integrated framework for the automation of citation collection and screening in systematic reviews. 
authors:
  - name: Angelo D'Ambrosio
    department: Institute for Infection Prevention and Hospital Hygiene
    affiliation: Freiburg University Hospital
    location: Freiburg, Germany
    email: angelo.d.ambrosio@uniklinik-freiburg.de; a.dambrosioMD@gmail.com
  - name: Hajo Grundmann
    department: Institute for Infection Prevention and Hospital Hygiene
    affiliation: Freiburg University Hospital
    location: Freiburg, Germany
    email: hajo.grundmann@uniklinik-freiburg.de
  - name: Tjibbe Donker
    department: Institute for Infection Prevention and Hospital Hygiene
    affiliation: Freiburg University Hospital
    location: Freiburg, Germany
    email: tjibbe.donker@uniklinik-freiburg.de
abstract: |
  The exponential and prolific growth of published original scientific contributions makes secondary literature abridgements increasingly demanding.
  We introduce a new open-source framework for systematic reviews that significantly reduces time and human resource allocation for text identification, collection, and screening of scientific literature.\
  The framework provides three main tools:
  1) an automatic citation search engine and manager that allows collecting records from multiple citation databases (Pubmed, WOS, SCOPUS, EMBASE, IEEE) with a unified query syntax,
  2) a citation screening tool based on Bayesian active machine learning and natural language processing that requires users feedback only on uncertain classifications to iteratively increase predictive accuracy and,
  3) a semi-automatic, data-driven query generator to create new search queries from existing reviewed citation data sets.\
  The framework was tested on an example topic to collect and screen citations of related scientific production.
  To evaluate the performance of the active machine learning classifier,
  we estimated the median posterior sensitivity and efficiency [90% Credible Intervals] using Bayesian simulation to predict the distribution of potentially relevant matches among the records not manually reviewed.\
  A total of 17,755 unique records were collected through the framework citation manager;
  101 of 766 records were found to be relevant after manual evaluation,
  while the rest were excluded by automatic classification;
  the theoretical efficiency was 95.6% [95.3%, 95.7%] with a sensitivity of 100% [93.5%, 100%].\
  A new search query was generated from the labelled dataset, and 82,579 additional records were collected;
  only 567 records required human review after automatic screening, and six additional positive matches were found.
  Including the additional records, the overall expected sensitivity decreased to 97.3% [73.8%, 100%] while the efficiency increased to 98.6% [98.2%, 98.7%].\
  For large studies, the framework can significantly reduce the human resources required to conduct systematic reviews
  by simplifying citation collection and screening while demonstrating exceptional sensitivity.
  Such a tool can improve the standardization and repeatability of systematic reviews.
keywords:
  - Systematic review automation
  - Citation management
  - Online data collection
  - Active machine learning
  - Natural language processing
  - Bayesian modeling
bibliography: references.bib
lang: en-GB
output: 
  rticles::arxiv_article:
    number_sections: no
    keep_tex: true
    includes:
      in_header: header.tex
---

### 2022-02-19 Manuscript/Manuscript.tex
update for arxiv submission

\begin{abstract}
The exponential and prolific growth of published original scientific
contributions makes secondary literature abridgements increasingly
demanding. We introduce a new open-source framework for systematic
reviews that significantly reduces time and human resource allocation
for text identification, collection, and screening of scientific
literature.\\
The framework provides three main tools: 1) An automatic citation search
engine and manager that allows collecting records from multiple citation
databases (Pubmed, WOS, SCOPUS, EMBASE, IEEE) with a unified query
syntax 2) A citation screening tool based on Bayesian active machine
learning and natural language processing that requires users feedback
only on uncertain classifications to iteratively increase predictive
accuracy and 3) A semi-automatic, data-driven query generator to create
new search queries from existing reviewed citation data sets.\\
The framework was tested on an example topic to collect and screen
citations of related scientific production. To evaluate the performance
of the active machine learning classifier, we estimated the median
posterior sensitivity and efficiency {[}90\% Credible Intervals{]} using
Bayesian simulation to predict the distribution of potentially relevant
matches among the records not manually reviewed.\\
A total of 17,755 unique records were collected through the framework
citation manager; 101 of 766 records were found to be relevant after
manual evaluation, while the rest were excluded by automatic
classification; the theorethical efficiency was 95.6\% {[}95.3\%,
95.7\%{]} with a sensitivity of 100\% {[}93.5\%, 100\%{]}.\\
A new search query was generated from the labelled dataset, and 82,579
additional records were collected; only 567 records required human
review after automatic screening, and six additional positive matches
were found. Including the additional records, the overall expected
sensitivity decreased to 97.3\% {[}73.8\%, 100\%{]} while the efficiency
increased to 98.6\% {[}98.2\%, 98.7\%{]}.\\
For large studies, the framework can significantly reduce the human
resources required to conduct systematic reviews by simplifying citation
collection and screening while demonstrating exceptional sensitivity.
Such tool can improve the standardization and repeatability of
systematic reviews.
\end{abstract}

@@

\begin{figure}
\centering
\includegraphics{Manuscript_files/figure-latex/performance plot-1.pdf}
\caption{\textbf{Figure 2}. Observed cumulative number of positive
matches (red dots) sorted by simple query ordering. The {[}trunc. 90\%
PrI{]} of the cumulative positive matches estimated by the logistic
Bayesian model is shown as a shaded area delimited by the 95\% quantile
of the PrI and by the observed number of positive matches (light blue
lines). The median of the PrI is represented by a darker blue line.}
\end{figure}

>>>>

\begin{abstract}
The exponential and prolific growth of published original scientific
contributions makes secondary literature abridgements increasingly
demanding. We introduce a new open-source framework for systematic
reviews that significantly reduces time and human resource allocation
for text identification, collection, and screening of scientific
literature.\\
The framework provides three main tools: 1) an automatic citation search
engine and manager that allows collecting records from multiple citation
databases (Pubmed, WOS, SCOPUS, EMBASE, IEEE) with a unified query
syntax, 2) a citation screening tool based on Bayesian active machine
learning and natural language processing that requires users feedback
only on uncertain classifications to iteratively increase predictive
accuracy and, 3) a semi-automatic, data-driven query generator to create
new search queries from existing reviewed citation data sets.\\
The framework was tested on an example topic to collect and screen
citations of related scientific production. To evaluate the performance
of the active machine learning classifier, we estimated the median
posterior sensitivity and efficiency {[}90\% Credible Intervals{]} using
Bayesian simulation to predict the distribution of potentially relevant
matches among the records not manually reviewed.\\
A total of 17,755 unique records were collected through the framework
citation manager; 101 of 766 records were found to be relevant after
manual evaluation, while the rest were excluded by automatic
classification; the theoretical efficiency was 95.6\% {[}95.3\%,
95.7\%{]} with a sensitivity of 100\% {[}93.5\%, 100\%{]}.\\
A new search query was generated from the labelled dataset, and 82,579
additional records were collected; only 567 records required human
review after automatic screening, and six additional positive matches
were found. Including the additional records, the overall expected
sensitivity decreased to 97.3\% {[}73.8\%, 100\%{]} while the efficiency
increased to 98.6\% {[}98.2\%, 98.7\%{]}.\\
For large studies, the framework can significantly reduce the human
resources required to conduct systematic reviews by simplifying citation
collection and screening while demonstrating exceptional sensitivity.
Such a tool can improve the standardization and repeatability of
systematic reviews.
\end{abstract}

@@

\begin{figure}
\centering
\includegraphics{Manuscript_files/figure-latex/performance_plot-1.pdf}
\caption{\textbf{Figure 2}. Observed cumulative number of positive
matches (red dots) sorted by simple query ordering. The {[}trunc. 90\%
PrI{]} of the cumulative positive matches estimated by the logistic
Bayesian model is shown as a shaded area delimited by the 95\% quantile
of the PrI and by the observed number of positive matches (light blue
lines). The median of the PrI is represented by a darker blue line.}
\end{figure}

### 2022-02-19 Manuscript/Manuscript_Results.Rmd
update for arxiv submission

```{r load framework, cache.rebuild=TRUE, include=FALSE}
source(file.path("R", "Setup.R"), local = knitr::knit_global())

@@

```{r session 1}

@@

```{r session 2}
new_query <- import_data("Session_journal.csv") %>%
  filter(Session_ID == "Session2") %>%
  with(Query[1])

@@

```{r performance plot, cache = FALSE, fig.width=7.5, fig.height=4.5, fig.cap="**Figure 2**. Observed cumulative number of positive matches (red dots) sorted by simple query ordering. The [trunc. 90% PrI] of the cumulative positive matches estimated by the logistic Bayesian model is shown as a shaded area delimited by the 95% quantile of the PrI and by the observed number of positive matches (light blue lines). The median of the PrI is represented by a darker blue line."}

>>>>

```{r load_framework, cache.rebuild=TRUE, include=FALSE}
source(file.path("R", "Setup.R"), local = knitr::knit_global())

@@

```{r session_1}

@@

```{r session_2}
new_query <- import_data("Session_journal.csv") %>%
  filter(Session_ID == "Session2") %>%
  with(Query[1])

@@

```{r performance_plot, cache = FALSE, fig.width=7.5, fig.height=4.5, fig.cap="**Figure 2**. Observed cumulative number of positive matches (red dots) sorted by simple query ordering. The [trunc. 90% PrI] of the cumulative positive matches estimated by the logistic Bayesian model is shown as a shaded area delimited by the 95% quantile of the PrI and by the observed number of positive matches (light blue lines). The median of the PrI is represented by a darker blue line."}

### 2022-02-19 Manuscript/S1.Protocol.Rmd
update for arxiv submission

---
title: "Study protocol"
date: "`r lubridate::today()`"
output:
  pdf_document:
    toc: yes
  github_document:
    toc: yes
---

@@

```{r query creation}

@@

```{r perform searches}
# This call will perform an API search on Pubmed, WOS and IEEE services and/or
# (based on the `actions` argument) parse already downloaded data (in our case,
# additional Pubmed results and Embase and Scopus results) manually added to the
# Session1/Query1 folder.

@@

```{r managing records}
# Extract the file paths of records. Arguments can be used to filter by session
# query, source. Only parsed files will be returned, not the raw ones downloaded
# manually.
Annotation_data <- extract_source_file_paths(journal) %>%
  # Read record files. Will parse them if raw data is downloaded manually (not
  # necessary in this case). Return a list of records, one per file.
  read_bib_files() %>%
  # Join a list of records into one dataframe, solving duplicated records
  join_records() %>%
  # Order records by the relative frequency of the query terms in the title +
  # abstract text. Increases the chance of encountering relevant records at the
  # beginning of the manual classification.
  order_by_query_match(query) %>%
  # Add fields for the manual classification
  mutate(
    Rev_manual = NA, # Where the first manual classification will be made
    Rev_prediction = NA, # Column for the evaluation of the predicted classes
    .before = DOI
  )
```

@@

```{r save annotation file}
# This function extracts the appropriate file paths from a session journal. By
# default it passes all stored files, otherwise it can be filtered by session,
# query, and source (i.e. Pubmed, WOS, IEEE)
record_files <- extract_source_file_paths(journal)

@@

```{r create session}
# Create the first session
create_session(Annotation_data, session_name = "Session1")
```

@@

```{r one call}
# First, create the Records/Session1/Query1 folder and put the manually
# downloaded records there if there are any. Otherwise, the folders will be
# created automatically during the API search

@@

```{r automatic annotation}
New_annotations <- enrich_annotation_file("Session1")
```

@@

```{r replication limits}
list(
  stop_after = 4,
  pos_target = NULL,
  labeling_limit = NULL
)
```

@@

```{r new query generation}

@@

```{r second session query}
query <- "(((Donker T) NOT (bacterium isolate)) OR ((network patient) AND
(resistant staphylococcus aureus) NOT (monte carlo) NOT isolation) OR
(facility AND (network patient) AND regional NOT hospitals NOT increase NOT
(patient transport) NOT (control infection use)) OR ((patient transport) NOT
(Donker T) NOT worker) OR (hospitals AND (network patient) NOT
(patient transport) NOT regional NOT clinical) OR (facility AND
(network patient) NOT hospitals NOT (patient transport) NOT regional NOT
prevention NOT medical) OR ((healthcare facility) NOT (Donker T) NOT
worker NOT positive) OR (hospitals NOT (network patient) NOT medical NOT
environmental NOT outcome NOT global) OR ((network patient) NOT facility NOT
hospitals NOT (patient transport) NOT therapy NOT global)) AND
((antimicrobial resistance) OR (healthcare infection))"
```

@@

```{r new annotation session}

@@

```{r grid search}
Grid_search <- perform_grid_evaluation(
  records,
  sessions_folder = "Grid_Search",
  prev_classification = records,
  ## Model parameters (can be changed by users)
  resample = c(FALSE, TRUE),
  n_init = c(50, 100, 250, 500),
  n_models = c(1, 5, 10, 20, 40, 60),
  pos_mult = c(1, 10, 20),
  pred_quants = list(
    c(.1, .5, .9),
    c(.05, .5, .95),
    c(.01, .5, .99)
  )
)
```

>>>>

---
title: "Study protocol"
date: "`r lubridate::today()`"
output:
  pdf_document:
    keep_tex: true
    toc: yes
  github_document:
    toc: yes
---

@@

```{r query_creation}

@@

```{r perform_searches}
# This call will perform an API search on Pubmed, WOS and IEEE services and/or
# (based on the `actions` argument) parse already downloaded data (in our case,
# additional Pubmed results and Embase and Scopus results) manually added to the
# Session1/Query1 folder.

@@

```{r managing_records}
# Extract the file paths of records. Arguments can be used to filter by session
# query, source. Only parsed files will be returned, not the raw ones downloaded
# manually.
Annotation_data <- extract_source_file_paths(journal) %>%
  # Read record files. Will parse them if raw data is downloaded manually (not
  # necessary in this case). Return a list of records, one per file.
  read_bib_files() %>%
  # Join a list of records into one dataframe, solving duplicated records
  join_records() %>%
  # Order records by the relative frequency of the query terms in the title +
  # abstract text. Increases the chance of encountering relevant records at the
  # beginning of the manual classification.
  order_by_query_match(query) %>%
  # Add fields for the manual classification
  mutate(
    Rev_manual = NA, # Where the first manual classification will be made
    Rev_prediction = NA, # Column for the evaluation of the predicted classes
    .before = DOI
  )
```

@@

```{r save_annotation file}
# This function extracts the appropriate file paths from a session journal. By
# default it passes all stored files, otherwise it can be filtered by session,
# query, and source (i.e. Pubmed, WOS, IEEE)
record_files <- extract_source_file_paths(journal)

@@

```{r create_session}
# Create the first session
create_session(Annotation_data, session_name = "Session1")
```

@@

```{r one_call}
# First, create the Records/Session1/Query1 folder and put the manually
# downloaded records there if there are any. Otherwise, the folders will be
# created automatically during the API search

@@

```{r automatic_annotation}
New_annotations <- enrich_annotation_file("Session1")
```

@@

```{r replication_limits}
list(
  stop_after = 4,
  pos_target = NULL,
  labeling_limit = NULL
)
```

@@

```{r new_query_generation}

@@

```{r second_session_query}
query <- "(((Donker T) NOT (bacterium isolate)) OR ((network patient) AND
(resistant staphylococcus aureus) NOT (monte carlo) NOT isolation) OR
(facility AND (network patient) AND regional NOT hospitals NOT increase NOT
(patient transport) NOT (control infection use)) OR ((patient transport) NOT
(Donker T) NOT worker) OR (hospitals AND (network patient) NOT
(patient transport) NOT regional NOT clinical) OR (facility AND
(network patient) NOT hospitals NOT (patient transport) NOT regional NOT
prevention NOT medical) OR ((healthcare facility) NOT (Donker T) NOT
worker NOT positive) OR (hospitals NOT (network patient) NOT medical NOT
environmental NOT outcome NOT global) OR ((network patient) NOT facility NOT
hospitals NOT (patient transport) NOT therapy NOT global)) AND
((antimicrobial resistance) OR (healthcare infection))"
```

@@

```{r new_annotation_session}

@@

```{r grid_search}
Grid_search <- perform_grid_evaluation(
  records,
  sessions_folder = "Grid_Search",
  prev_classification = records,
  ## Model parameters (can be changed by users)
  resample = c(FALSE, TRUE),
  n_init = c(50, 100, 250, 500),
  n_models = c(1, 5, 10, 20, 40, 60),
  pos_mult = c(1, 10, 20),
  pred_quants = list(
    c(.1, .5, .9),
    c(.05, .5, .95),
    c(.01, .5, .99)
  )
)
```

### 2022-02-19 Manuscript/S2.Additional_outputs.Rmd
update for arxiv submission

---
title: "S2. Additional figures and table"
date: "`r lubridate::today()`"
output:
  pdf_document:
    toc: yes
    includes:
      in_header: header.tex
  github_document:
    toc: yes
---

@@

```{r posterior distributions, fig.width=10, fig.height=10, fig.cap="**Figure 1**. Mixture predictive distribution of the probability of a positive match, grouped by labelling status."}

>>>>

---
title: "S2. Additional figures and table"
date: "`r lubridate::today()`"
output:
  pdf_document:
    toc: yes
    keep_tex: true
    includes:
      in_header: header.tex
  github_document:
    toc: yes
---

@@

```{r posterior_distributions, fig.width=10, fig.height=10, fig.cap="**Figure 1**. Mixture predictive distribution of the probability of a positive match, grouped by labelling status."}
